\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=0.6in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\thispagestyle{empty}

\definecolor{primary}{RGB}{0,0,0}
\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\titlerule]
\setlist[itemize]{noitemsep,leftmargin=*,topsep=2pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Bhim Prasad Lamichhane}} \\[0.5em]
    \small {Software Engineer | Full Stack Engineer | QA Automation Engineer} \\[0.5em]
    \href{mailto:dreamypd73@gmail.com}{dreamypd73@gmail.com} |
    \href{tel:+9779814495185}{+977 9814495185} | Kathmandu, Nepal \\[0.5em]
 
    Github: \href{https://github.com/bhimpd/}{https://github.com/bhimpd/} \\
    LinkedIn: \href{https://www.linkedin.com/in/bhim-pd-lamichhane-a8275819b/}{linkedin.com/in/bhim-pd-lamichhane-a8275819b}
\end{center}

\noindent Motivated Full Stack Engineer with hands-on experience in web development, backend systems, QA automation, and digital banking applications. Skilled in building scalable solutions using modern frameworks, performing end-to-end testing, API validation, automation scripting, and ensuring high-quality software delivery.

\section*{Technical Skills}
\begin{itemize}
    \item \textbf{Frontend:} HTML, CSS, JavaScript, Bootstrap, ReactJS
    \item \textbf{Backend:} PHP, JavaScript, Node.js, Laravel, Java
    \item \textbf{Database:} MySQL, Postgres, MongoDB
    \item \textbf{Others:} Cypress, Playwright, Selenium, JMeter, Postman, BurpSuite, GitHub, ClickUp, Apidog, Docker, Linux, Magento2, RESTful APIs, Netsuite, Appium
\end{itemize}

\section*{Professional Experience}

\textbf{InfoDevelopers Pvt. Ltd.} | QA Automation Engineer \hfill July 2025 -- Present \\
\textit{Technologies: Postman, Burp Suite, JMeter, Playwright, GitHub,Playwright, Appium, Azure DevOps}

\begin{itemize}
    \item Performed end-to-end testing for E-Banking and Mobile Banking applications including login, transaction flows, customer, bank and cooperatives registration , digital finance services, wallet operations, and fund transfer.
    \item Tested major modules such as Digital Finance Services, Utility \& Bill Payments, Topup, Electricity, Government Payments, Bluebook Renewal, and Travel \& Ticketing Services (Airlines, Bus, Cable Car, Movies).
    \item Worked extensively on the Payment Gateway (PG), which serves as a middleware between CBS (Core Banking System) and Mobile Banking.
    \item Validated key PG functionalities including:
          \begin{itemize}
             \item Cooperative bank onboarding and account setup.
             \item Service enablement for each cooperative (SMS alerts, utility services, ticketing, etc.).
             \item Transaction processing, settlement reports, and configuration management.
          \end{itemize}
    \item Collaborated with CBS teams to verify customer registration, account creation, service activation, beneficiary setup, loan/payment validations, and transaction processing.
    \item Conducted manual and automation testing using Playwright for banking portal and PG modules.
    \item Performed API testing and automation using Postman (collections, scripting, environments, and data-driven tests).
    \item Executed security testing using Burp Suite including request interception, authorization checks, and vulnerability scanning.
    \item Conducted UI/UX testing, regression testing, integration testing, and cross-device validation for stable and high-quality releases.
\end{itemize}


\textbf{Intuji Pvt. Ltd.} | Trainee Software Engineer \& QA Automation Engineer \hfill May 2024 -- July 2025 \\
\textit{Technologies: PHP, Laravel, JavaScript, Node.js, Magento2, Netsuite, Docker, Cypress, Postman, GitHub, ClickUp}

\begin{itemize}
    \item Worked on large-scale \textbf{E-commerce and CMS-based applications}, contributing to both development and quality assurance activities.
    \item Developed and enhanced \textbf{Magento 2 functionalities}, including custom pages, blocks, models, and reusable components.
    \item Designed and integrated \textbf{RESTful APIs} for multiple application modules and business workflows.
    \item Refactored existing codebases to improve \textbf{maintainability, performance, and code quality}.
    \item Upgraded Magento projects to newer versions, ensuring \textbf{security, compatibility, and functional stability}.
    \item Performed complete \textbf{E-commerce testing lifecycle}, including website functionality, responsiveness, CMS operations, and checkout flows.
    \item Automated \textbf{CMS CRUD operations} (product creation, update, deletion, publishing) and validated data consistency on the live website.
    \item Automated \textbf{end-to-end user journeys} such as product listing, cart management, checkout, shipping, and order confirmation using \textbf{Cypress}.
    \item Designed and implemented a \textbf{generic, reusable automation framework} to support scalable regression testing across projects.
    \item Conducted extensive \textbf{manual testing}, including functional, regression, exploratory, and UI/UX testing.
    \item Created and maintained detailed \textbf{manual test cases} aligned with business requirements.
    \item Performed \textbf{API testing (manual and automated)} using Postman for backend validation.
    \item Documented test scenarios, reported defects, and collaborated with developers using \textbf{ClickUp}.
    \item Gained strong hands-on experience in \textbf{software testing, quality assurance practices, and test automation}.
\end{itemize}

\textbf{Intuji Pvt. Ltd.} | Intern \hfill Jan 2024 -- Apr 2024 \\
\textit{Technologies: HTML, CSS, JS, PHP, MySQL, Postman, Magento2, Cypress}

\begin{itemize}
    \item Developed and integrated \textbf{RESTful APIs} for multiple project modules.
    \item Worked on \textbf{Magento-based applications}, creating custom pages, blocks, models, and backend functionalities.
    \item Assisted in backend development tasks, database operations, and API validation.
    \item Performed \textbf{manual testing} for newly developed features and gained hands-on experience in QA processes.
    \item Gained foundational knowledge of \textbf{test automation concepts} and best practices for software quality assurance.
    \item Collaborated with senior developers and QA engineers to understand full \textbf{development-to-testing workflows}.
\end{itemize}


\textbf{S.A.I.T} | Frontend Developer \hfill Feb 2023 -- Dec 2023 \\
\textit{Technologies: HTML, CSS, SCSS, Bootstrap, JS, PHP, MySQL, GitHub}

\begin{itemize}
    \item Developed interactive and mobile-responsive websites.
    \item Improved SEO performance through optimization and code enhancements.
\end{itemize}

\section*{Education}
\textbf{Bachelor's in Computer Science and Information Technology} | Tribhuvan University \hfill 2019 -- 2024 \\
Percentage: 72 \\


\section*{Projects}

\textbf{\href{https://bhimassignment.netlify.app/}{E-commerce Project}} | HTML, CSS, Bootstrap, JS, React \\
Developed an e-commerce platform with product listing, search, filtering, and add-to-cart functionality.

\noindent\textbf{\href{https://github.com/bhimpd/Online-Voting-System}{Online Voting System}} | PHP, Laravel, MySQL \\
Created a full-feature online voting platform with group voting, CRUD operations for voters \& groups.

\noindent\textbf{\href{https://github.com/bhimpd/laravel_2ndecommerce}{E-commerce Website}} | Laravel, Blade, MySQL \\
Developed a dynamic e-commerce system with admin-controlled product management.

\noindent\textbf{\href{https://github.com/bhimpd/toolfix_automation}{Cypress Automation}} | Cypress \\
Developed a complete E2E automation suite covering authentication, CRUD flows, CMS modules, and regression scenarios using reusable page objects, custom commands, and fixtures.

\noindent\textbf{\href{https://github.com/bhimpd/playwright_automation}{Playwright Web Automation}} | Playwright \\
Built scalable automation scripts using Page Object Model (POM) to test login flows, admin modules, form validations, and multi-page navigation. Implemented waits, reporting, retries, and test hooks.  

\begin{itemize}
    \item Integrated **CI/CD pipelines using Jenkins** to automate build, test, and report generation.
    \item Ensured **end-to-end automation**, from code commit to reporting, improving release efficiency and test reliability.
\end{itemize}


\noindent\textbf{\href{https://github.com/bhimpd/Banking-Portal}{Banking Portal Automation}} | Playwright \\
Automated core modules of a banking portal including:
\begin{itemize}
    \item Login Module with negative + positive test coverage
    \item Global Setup Parameters module including add/edit/update flows
    \item Cover Positive Case \& Negative Case Scenerios and Handle the Error Validation
    \item Implemented POM, fixtures, reusable actions, and data-driven testing
\end{itemize}

\noindent\textbf{\href{https://github.com/bhimpd/Payment-Gateway}{Payment Gateway Automation}} | Playwright \\
Designed automation for PG (middleware between CBS and mobile banking) focusing on:
\begin{itemize}
    \item Secure Login Module automation with credential validation
    \item Credentials Setup Module automation (CRUD Operatoin for  New Bank with their primary account and secondary account)
    \item Implemented POM, fixtures, reusable actions, and data-driven testing
    \item Error-handling with Positive and Negative Test Case Scenerio testing
\end{itemize}

\noindent\textbf{\href{https://github.com/bhimpd/playwright_api_automation}{Playwright API Automation Framework}} | Playwright \\
Developed a complete API automation framework using Playwright

\noindent\textbf{\href{https://github.com/bhimpd/mble_automation_to_do_app}{Mobile Automation – ToDo App}} | WebdriverIO, Appium, TypeScript \\
Developed a full mobile automation suite for an Android ToDo application. The automation workflow includes:
\begin{itemize}
    \item Integration of WebdriverIO with Appium to interact with Android devices.
    \item Automated app launch, UI interactions, and functional validations.
  \item Automated **parallel execution across multiple Android devices** to ensure cross-device compatibility.
    \item Integration with **Allure reporting framework** for detailed test execution analysis, dashboards, and result visualization.
    \item Automated app launch, UI interactions, and functional validations.\end{itemize}


\end{document}
